\LARGE \bf The Battle for Filter Supremacy: A Retrospective: The Movie: The Game: The Paper

### 2014-12-12 Report/project_report.tex
Added more stuff to state parametrization and augmentation

\subsection{State Parametrization}
As described in Section \ref{sec:experiments}, we evaluated the MSCKF using a dataset in which the IMU `measures' gravity-corrected linear velocities rather than raw linear accelerations.
In order to accommodate this alternative state parametrization, the mathematical framework described in this section differs slightly from that described in \cite{Mourikis:2007:ICRA}.

In our implementation, we parametrize the IMU state at time $k$ as the 13-dimensional vector
\begin{align}
    \Vec{x}_{I,k} &= \bbm \Vec{q}_{IG,k} & \Vec{b}_{\boldsymbol{\omega},k} & \Vec{b}_{\Vec{v},k} & \Vec{p}_{G,k}^{IG} \ebm^T
\end{align}
where $\Vec{q}_{IG,k}$ is the unit quaternion representing the rotation from the global frame $\mathcal{F}_G$ to the IMU frame $\mathcal{F}_I$, $\Vec{b}_{\boldsymbol{\omega},k}$ is the bias on the gyro measurements $\boldsymbol{\omega}_m$, $\Vec{b}_{\Vec{v},k}$ is the bias on the velocity measurements $\Vec{v}_m$, and $\Vec{p}_{G,k}^{IG}$ is the vector from the origin of $\mathcal{F}_G$ to the origin of $\mathcal{F}_I$ expressed in $\mathcal{F}_G$ (i.e., the position of the IMU in the global frame).

At time $k$, the full state of the MSCKF consists of the current IMU state estimate, and estimates of $N$ past camera poses in which active feature tracks were visible:
\begin{align}
    \hat{\Vec{x}}_k &= \bbm \hat{\Vec{x}}_{I,k} & \hat{\Vec{q}}_{C_1 G} & \hat{\Vec{p}}_G^{C_1 G} & \hdots & \hat{\Vec{q}}_{C_N G} & \hat{\Vec{p}}_G^{C_N G} \ebm ^T
\end{align}.

@@

>>>>

\subsection{MSCKF State Parametrization}
We evaluated the MSCKF using a dataset in which the IMU `measures' gravity-corrected linear velocities rather than raw linear accelerations(see Section \ref{sec:experiments}).
In order to accommodate this alternative state parametrization, the mathematical framework described in this section differs slightly from that described in \cite{Mourikis:2007:ICRA}.

In our implementation, we parametrize the IMU state at time $k$ as the 13-dimensional vector
\begin{align}
    \Vec{x}_{I,k} &= \bbm \Vec{q}_{IG,k}^T & \Vec{b}_{\boldsymbol{\omega},k}^T & \Vec{b}_{\Vec{v},k}^T & \Vec{p}_{G,k}^{IG \hspace{0.3em} T} \ebm^T
\end{align}
where $\Vec{q}_{IG,k}$ is the unit quaternion representing the rotation from the global frame $\mathcal{F}_G$ to the IMU frame $\mathcal{F}_I$, $\Vec{b}_{\boldsymbol{\omega},k}$ is the bias on the gyro measurements $\boldsymbol{\omega}_m$, $\Vec{b}_{\Vec{v},k}$ is the bias on the velocity measurements $\Vec{v}_m$, and $\Vec{p}_{G,k}^{IG}$ is the vector from the origin of $\mathcal{F}_G$ to the origin of $\mathcal{F}_I$ expressed in $\mathcal{F}_G$ (i.e., the position of the IMU in the global frame).

At time $k$, the full state of the MSCKF consists of the current IMU state estimate, and estimates of $N$ past camera poses in which active feature tracks were visible:
\begin{align}
    \hat{\Vec{x}}_k &= \bbm \hat{\Vec{x}}_{I,k}^T & \hat{\Vec{q}}_{C_1 G}^T & \hat{\Vec{p}}_G^{C_1 G \hspace{0.3em} T} & \hdots & \hat{\Vec{q}}_{C_N G}^T & \hat{\Vec{p}}_G^{C_N G \hspace{0.3em} T} \ebm ^T
\end{align}

We can also define the MSCKF ``error state'' at time $k$:
\begin{align}
    \tilde{\Vec{x}}_k &= \bbm \tilde{\Vec{x}}_{I,k}^T & \boldsymbol{\delta\theta}_{C_1}^T & \tilde{\Vec{p}}_G^{C_1 G \hspace{0.3em} T} & \hdots & \boldsymbol{\delta\theta}_{C_N}^T & \tilde{\Vec{p}}_G^{C_N G \hspace{0.3em} T} \ebm ^T
\end{align}
where
\begin{align}
    \tilde{\Vec{x}}_{I,k} &= \bbm \boldsymbol{\delta\theta}_I^T & \tilde{\Vec{b}}_{\boldsymbol{\omega},k}^T & \tilde{\Vec{b}}_{\Vec{v},k}^T & \tilde{\Vec{p}}_{G,k}^{IG \hspace{0.3em} T} \ebm^T
\end{align}
is the 12-dimensional IMU error state.
In the above, $\tilde{x}$ denotes the difference between the true value and the estimated value of the quantity $x$.
The rotational errors $\boldsymbol{\delta\theta}$ are defined according to
\begin{align*}
    \boldsymbol{\delta}\Vec{q} &= \hat{\Vec{q}}^{-1} \otimes \Vec{q} \simeq \bbm \frac{1}{2}\boldsymbol{\delta\theta}^T & 1 \ebm^T.
\end{align*}

Accordingly, the MSCKF state covariance $\hat{\Vec{P}}_k$ is a $(12+6N)\times(12+6N)$ matrix that may be partitioned as
\begin{align}
    \hat{\Vec{P}}_k &= \bbm \hat{\Vec{P}}_{II,k} & \hat{\Vec{P}}_{IC,k} \\ \hat{\Vec{P}}_{IC,k}^T & \hat{\Vec{P}}_{CC,k} \ebm
\end{align}
where $\hat{\Vec{P}}_{II,k}$ is the $12\times12$ covariance matrix of the current IMU state, $\hat{\Vec{P}}_{CC,k}$ is the $6N\times6N$ covariance matrix of the camera poses, and $\hat{\Vec{P}}_{IC,k}$ is the $12\times6N$ cross-correlation between the current IMU state and the camera poses.

\subsection{MSCKF State Augmentation}
When a new camera image becomes available, the MSCKF state must be augmented with the current camera state.
We obtain the camera state by applying the known transformation $\left(\Vec{q}_{CI}, \Vec{p}_I^{CI}\right)$ to a copy of the current IMU state:
\begin{align}
    \hat{\Vec{q}}_{C_{N+1} G} &= \Vec{q}_{CI} \otimes \hat{\Vec{q}}_{IG,k} \\
    \hat{\Vec{p}}_G^{C_{N+1}G} &= \hat{\Vec{p}}_G^{IG} + \hat{\Vec{C}}_{IG,k} \hat{\Vec{p}}_I^{CI}
\end{align}
where $\hat{\Vec{C}}_{IG,k}$ is the rotation matrix corresponding to $\hat{\Vec{q}}_{IG,k}$ and $\otimes$ denotes quaternion multiplication.

Assuming the MSCKF state has already been augmented by $N$ camera poses, we add the $\left(N+1\right)^\text{th}$ camera pose to the state as follows:
\begin{align}
    \hat{\Vec{x}}_k &\leftarrow \bbm \hat{\Vec{x}}_k^T & \hat{\Vec{q}}_{C_{N+1} G}^T & \left(\hat{\Vec{p}}_G^{C_{N+1}G}\right)^T \ebm^T
\end{align}

We must also augment the MSCKF state covariance:
\begin{align}
    \hat{\Vec{P}}_k &\leftarrow \bbm \Vec{1}_{12+6N} \\ \Vec{J}_k \ebm \hat{\Vec{P}}_k \bbm \Vec{1}_{12+6N} \\ \Vec{J}_k \ebm^T
\end{align}
where the Jacobian $\Vec{J}_k$ is given by
\begin{align}
\Vec{J}_k &= \bbm \hat{\Vec{C}}_{C I, k} & \Vec{0}_{3\times6} & \Vec{0}_{3\times3} & \Vec{0}_{3\times6N} \\
                            \left(\hat{\Vec{C}}_{I G, k}^T \Vec{p}_{I,k}^{CI}\right)^\times & \Vec{0}_{3\times6} & \Vec{1}_3 & \Vec{0}_{3\times6N}
                \ebm
\end{align}

@@

\subsection{MSCKF State Covariance Propagation}
